How do we get from object recognition\\ to object naming?

### 2018-07-09 papers/SiVL2018/resources.tex
adds resource discussion

\begin{table*}[t]
	\begin{tabular}{|l||l|c|c|c|c|}
		\hline
		Resource
		& Purpose 	& \#Cat 	
		& \multicolumn{2}{c|}{Constraints on} 
		& WordNet  \\
			&			
		& 			
		& language 	& images 
		& IDs?\\
		\hline \hline
		\refcoco 	& REG,REC& 80 		& -				
					& $\geq$2 objects of same cat 
					& \xmark \\
		\refcocop 	& REG,REC
					& 80		& + 			
					& $\geq$2 objects of same cat 
					& \xmark \\	
		\flickr 	& Phrase localization
					& ?				& -- 
					& & \xmark \\
					& Caption generation
					& & & &  \\
		\vgenome 	& Scene understanding 
					& 80k 
					& & & \cmark\\
					& Phrase localization
					& & & &  \\
		\hline
	\end{tabular}
	\caption{\label{tab:summary_resources} Intended to provide an overview of resources, their purpose/use and shortcomings wrt object naming. Cat: Categories; REG and REC: Referring expression generation and comprehension, respectively.}
\end{table*}

@@

\paragraph{\refcoco and \refcocop}~\\\cs{REF} 
Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}.

@@

\paragraph{VisualGenome}~\\
VisualGenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

@@

\paragraph{Solution to R1: Object detectors?}
An alternative would be to apply object detectors trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained object detectors only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
For the training of detectors using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.

\paragraph{\flickr}
By design, \flickr can be used to study the way people refer to individual entities in an image in dependence on the situation the speakers describe. 
In contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
We can therefore gather naturally produced object names from the data and may be able to infer their entry-level categories. 
This is only the case for objects which are mentioned in the captions though, which is why \flickr does not fully satisfy requirement~R2.

\flickr does not meet requirement R1 for similar reasons as \refcoco(+). 
Object categories tend to be even less specific than those of COCO, they include, e.g.,~\cs{TODO; people...}.

Note that \flickr is less suited for referring expression generation and interpretation\cs{use the term grounding, interpretation or understanding to refer to the process of linking language to an image region?}, though, in that the mentions in isolation of their linguistic context may not uniquely identify the referred object.

\paragraph{Visual Genome}
From a linguistic perspective, object categories (e.g.,~\cat{fawn}, \cat{industrial park}, \cat{opened bag}, \cat{carpet oriental}) are defined pragmatically, and the annotations are rather unstructured. 
For example, as illustrated in Figure~\ref{fig:ex_visualgenome}, the categorization of expressions into one of the three annotation types (region, attributes and relationships), is based on the verbs (\word{is} denotes attributes) and prepositions (\word{at} or \word{in} denotes relationships) \cs{double-check w/ paper}
Note also the spelling mistakes (e.g.,~\word{dalmation}, \word{wating}). 
Furthermore, regions and their annotations are highly redundant in that expressions referring to the same object may still be linked to different bounding boxes\cs{We would need to, e.g., merge boxes through IoU $\geq$ some threshold}.

As far as object naming is concerned, requirement R1 is not met.    
The annotators were free in their choice of a name for the objects, hence, the latter is usually the entry-level in many annotations. 
For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, Visual Genome satisfies R2---we can infer the entry-level name of each object in the image. 
For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location. \\

\begin{figure}[t]
	\begin{center}
	\begin{minipage}{.37\textwidth}
		\includegraphics[scale=.25]{fig/visual_genome_dogs.png}
	\end{minipage}
	\begin{minipage}{.6\textwidth}
		\begin{tabular}{l|l}
			\hline
			Annotation	& \\	
			types		& 	\\
			\hline \hline
			Regions &  dalmatian's head; dalmatian dog\\
					& wating at a dinner table; the dog is gray\\
			Attributes & dog is gray; dalmation is eating\\
			Relationships & dog at table; dalmation IN chair; \\
							& heeler eating treat \\
							\hline
		\end{tabular}
	\end{minipage}
	\caption{Example of Visual Genome. \label{fig:ex_visualgenome}}
	\end{center}
\end{figure}

@@

\cs{XXXXX}\\\\
\subsubsection{Analysis}

We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
See \cite{Yu2016} for more details.

\subsection{\cs{Language Resources? (WordNet)}}

@@

>>>>

\begin{table*}[t]
	\begin{tabular}{|l||l|c|c|c|c|c|c|}
		\hline
		Resource
		& Purpose 	& \#Cat & \#Ref/ & \#Refs
		& \multicolumn{2}{c|}{Constraints on} 
		& WordNet  \\
		& & & object			
		& 			
		& language 	& images 
		& IDs?\\
		\hline \hline
		\refcoco 	& REG,REC
					& 80 & 3 & 50k
					& -				
					& $\geq$2 objs  
					& \xmark \\
					&
					& & & 
					& 
					& of same cat
					& \\
		\refcocop 	& REG,REC
					& 80 & 3 & 50k
					& + 			
					& $\geq$2 objs  
					& \xmark \\	
					&
					& & & 
					& 
					& of same cat
					& \\
		\flickr 	& Phrase localization
					& ?	& & 
					& -- 
					& & \xmark \\
					& Caption generation
					& & & &  \\
		\vgenome 	& Scene understanding 
					& 80k & & 
					& & & \cmark\\
					& Phrase localization
					& & & &  \\
		\hline
	\end{tabular}
	\caption{\label{tab:summary_resources} Overview of V\&L benchmarks for taks related to reference. Cat: Categories; Ref: Reference; REG and REC: Referring expression generation and comprehension, respectively.}
\end{table*}

@@

\paragraph{\refcoco and \refcocop \cite{Yu2016}}~\\ 
Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}.

@@

\paragraph{\vgenome}~\\
\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.

@@

\paragraph{Solution to R1: Object detectors?}
An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.

\paragraph{\flickr}
By design, \flickr can be used to study the way people refer to individual entities in an image in dependence on the situation the speakers describe. 
In contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
We can therefore gather naturally produced object names from the data and may be able to infer their entry-level categories. 
%
This is only the case for objects which are mentioned in the captions, which is why \flickr does not fully satisfy requirement~R2 \cs{ADD EXAMPLE IMAGE}.

\flickr does not meet requirement R1 for similar reasons as \refcoco(+). 
Object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene}).

Note that \flickr is less suited for referring expression generation and interpretation\cs{use the term grounding, interpretation or understanding to refer to the process of linking language to an image region?}, though, in that the mentions in isolation of their linguistic context may not uniquely identify the referred object. 
For example, the two men shown in the image in Figure~\ref{fig:ex_flickr} are  referred to by \refexp{a man} or \refexp{a guy}.

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.32\textwidth}
			\includegraphics[width=4cm]{fig/flickr_1000523639_boxes.jpg}
		\end{minipage}
		\begin{minipage}{.67\textwidth}	
				{
			\begin{tabular}{l}
				\hline
				\green{[EN$_{39}$ Two people]} in {[EN$_{45}$ the photo]} are playing\\
				\; \red{[EN$_{40}$ the guitar]} and {[EN$_{41}$ the other]} is poking at {[EN$_{0}$ him]} .\\

			\blue{[EN$_{42}$ A man]} in \yellow{[EN$_{43}$ green]} holds \red{[EN$_{40}$ a guitar]} while \\
			\;{[EN$_{41}$ the other man]} observes \yellow{[EN$_{43}$ his shirt]} .\\

		{[EN$_{41}$ A man]} is fixing \yellow{[EN$_{43}$ the guitar players costume]} .\\

	{[EN$_{41}$ a guy]} stitching up \yellow{[EN$_{43}$ another man 's coat]} .\\

	\green{[EN$_{39}$ the two boys]} playing \red{[EN$_{40}$ guitar]} \\
	\hline
			\end{tabular}
			}
		\end{minipage}

		\caption{Example of \flickr. \label{fig:ex_flickr}}
	\end{center}
\end{figure}

\paragraph{\vgenome}
From a linguistic perspective, object categories (e.g.,~\cat{fawn}, \cat{industrial park}, \cat{opened bag}, \cat{carpet oriental}) are defined pragmatically, and the annotations are rather unstructured. 
For example, as illustrated in Figure~\ref{fig:ex_visualgenome}, the categorization of expressions into one of the three annotation types (region, attributes and relationships), is based on the verbs (\word{is} denotes attributes) and prepositions (\word{at} or \word{in} denotes relationships) \cs{double-check w/ paper}
Note also the spelling mistakes (e.g.,~\word{dalmation}, \word{wating}). 
Furthermore, regions and their annotations are highly redundant in that expressions referring to the same object may still be linked to different bounding boxes\cs{We would need to, e.g., merge boxes through IoU $\geq$ some threshold}.

As far as object naming is concerned, requirement R1 is not met.    
The annotators were free in their choice of a name for the objects, hence, the latter is usually the entry-level in many annotations. 
For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, \vgenome satisfies R2---we can infer the entry-level name of each object in the image. 
For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location. \\

\begin{figure}[t]
	\begin{center}
	\begin{minipage}{.33\textwidth}
		\includegraphics[width=4cm]{fig/visual_genome_dogs.png}
	\end{minipage}
	\begin{minipage}{.65\textwidth}
		\begin{tabular}{l|l}
			\hline
			Annotation	& \\	
			types		& 	\\
			\hline \hline
			Regions &  dalmatian's head; dalmatian dog\\
					& wating at a dinner table; the dog is gray\\
			Attributes & dog is gray; dalmation is eating\\
			Relationships & dog at table; dalmation IN chair; \\
							& heeler eating treat \\
							\hline
		\end{tabular}
	\end{minipage}
	\caption{Example of \vgenome. \label{fig:ex_visualgenome}}
	\end{center}
\end{figure}

@@

\cs{XXXXX}\\\\

@@

\begin{table}[t]
	\begin{tabular}{lccc}
		\hline
		Resource & \multicolumn{3}{c}{No. categories $cat$ for which $*(cat, \text{ILSVRC})$:} \\
				& $\in$
				& superset
				& $\supset$\\
		\hline \hline
		\refcoco & 15 \\
		\refcocop & \\
		\flickr & \\
		\vgenome & \\
		\hline
	\end{tabular}
	\caption{Coverage of the categories by the $1,000$~synsets of the ILSVRC image classification challenge.  \label{tab:coverage_ilsvrc}}
\end{table}
